### 2024-04-18 docs/SOSP 2024/results.tex
Add new graphs

We evaluate \Treebeard{} on four different target processors, an NVIDIA RTX 4060 GPU (8GB RAM, CUDA 11.5),
an NVIDIA T400 GPU (2GB RAM, CUDA 11.5), an AMD MI210 GPU (64GB RAM, ROCm 4.5?) and an 
Intel Core i9-11900K CPU (16 virtual cores, 128 GB RAM). We compare \Treebeard{} with 
four other systems, NVIDIA RAPIDs v23.10, Tahoe, XGBoost v1.7.6 and \TreebeardOLD{} CPU. 
We measure both kernel time and total time (including data transfer to the GPU and results back) 
for RAPIDs and \Treebeard{}. Tahoe only allows us to measure the kernel time since it is written
as an executable that performs inference repeatedly on the same data that is transferred to the GPU once.

We use two sets of benchmarks to perform the comparison.
We use 8 real-world models trained on data from the Intel Machine 
Learning Benchmark suite~\cite{MLBenchmarks}. These models were also
used to evaluate \TreebeardOLD{}\cite{Treebeard}.
To enable more exhaustive evaluation we generated 700 random models with
varying number of trees (100---1000) and features (powers of two in the range 8---1024). 
Each tree has leaves at depths 2 to a maximum depth of 6, 7 or 8.

\subsection{Performance comparisons on NVIDIA GPUs}
\subsubsection*{Real-world models}
We performed a detailed performance comparison between \Treebeard{}, Tahoe, RAPIDS and XGBoost on the real-world benchmarks.
Figure~\ref{Fig:TBvsRAPIDsTahoe_4060_Speedup} shows the geomean speedup of \Treebeard{} at different batch sizes on RTX 4060. 
We do not show results for XGBoost since the speedups are an order of magnitude higher and too large to fit on the same graph.  
  The plot has lines for kernel time and total time speedup over RAPIDS and kernel time speedup over Tahoe. As can been seen \Treebeard{} is uniformly faster than Tahoe{\footnote{Tahoe does not support multiclass models and to enable comparison wet ran the multiclass models (\op{covtype} and \op{letters}) as regression models. We also noticed that some variants of Tahoe produce wrong results (as reported by its own tests) for 
  \op{letters} and \op{year}. In these cases, we pick the time of the fastest variant that gives the correct results.
}} by $2-3\times$ at all batch sizes. 
Compared to RAPIDS, \Treebeard{} is about $4\times$ faster at batch size 512. The relative performance of RAPIDs improves with batch size, but \Treebeard{} is still faster by $1.5-2\times$ evan at very high ($16K$) batch sizes. 
The plot also shows that the speedups are significant even when data needs to be transferred to the GPU and results need to be transferred back. They are lower than kernel time speedup as both systems have a constant additional transfer overhead.

@@

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
  \caption{Geomean speedup of schedule found by exploration heuristic vs best 4060 schedule on NVIDIA RTX 4060, NVIDIA T400 and AMD MI2160 across batch sizes}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_full_exp_vs_at.png}
  \caption{Schedule exploration heuristic exploration time speedup vs full schedule exploration}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{figure}

>>>>

We evaluate \Treebeard{} on four different target processors, an NVIDIA RTX 4060 GPU (8GB RAM, CUDA 11.5),
an NVIDIA T400 GPU (2GB RAM, CUDA 11.5), an AMD MI210 GPU (64GB RAM, ROCm 4.5\TODO{Check the version}) and an 
Intel Core i9-11900K CPU (16 virtual cores, 128 GB RAM). We compare \Treebeard{} with 
four other systems, NVIDIA RAPIDs v23.10, Tahoe, XGBoost v1.7.6 and \TreebeardOLD{} CPU. 
We measure both kernel time and total time (including data transfer to the GPU and results back) 
for RAPIDs and \Treebeard{}. Tahoe only allows us to measure the kernel time since it is written
as an executable that performs inference repeatedly on the same data that is transferred to the GPU once.

We use two sets of benchmarks to perform the comparison.
We use 8 real-world models trained on data from the Intel Machine 
Learning Benchmark suite~\cite{MLBenchmarks}. These models were also
used to evaluate \TreebeardOLD{}\cite{Treebeard}.
To enable more exhaustive evaluation we generated 700 random models with
varying number of trees (100---1000) and features (powers of two in the range 8---1024). 
Each tree has leaves at depths 2 to a maximum depth of 6, 7 or 8.
For \Treebeard{}, we use schedules found using the schedule exploration
heuristic (Section \ref{sec:exploring}) unless otherwise specified.

\subsection{Performance comparisons on NVIDIA GPUs}
\subsubsection*{Real-world models}
We performed a detailed performance comparison between \Treebeard{}, Tahoe, RAPIDS and XGBoost on the real-world benchmarks.
Figure~\ref{Fig:TBvsRAPIDsTahoe_4060_Speedup} shows the geomean speedup of \Treebeard{} at different batch sizes on RTX 4060. 
We do not show results for XGBoost since the speedups are an order of magnitude higher and too large to fit on the same graph.  
The plot has lines for kernel time and total time speedup over RAPIDS and kernel time speedup over Tahoe. As can been seen 
\Treebeard{} is uniformly faster than Tahoe{\footnote{Tahoe does not support multiclass models. To enable comparison, we ran 
the multiclass models (\op{covtype} and \op{letters}) as regression models only with Tahoe. We also noticed that some variants
of Tahoe produce wrong results (as reported by its own tests) for \op{letters} and \op{year}. In these cases, we pick the 
time of the fastest variant that gives the correct results.}} by $2-3\times$ at all batch sizes. 
Compared to RAPIDS, \Treebeard{} is about $4\times$ faster at batch size 512. The relative performance of RAPIDs improves 
with batch size, but \Treebeard{} is still faster by $1.5-2\times$ even at very high ($16K$) batch sizes. 
The plot also shows that the speedups are significant even when data needs to be transferred to the GPU and results need to
be transferred back. They are lower than kernel time speedup as both systems have a constant additional transfer overhead.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_bar_graph.png}
  \caption{\Treebeard{} vs RAPIDs and Tahoe kernel time and total time speedup on NVIDIA RTX 4060 for individual benchmarks (geomean over all batch sizes).
  \TODO{Add bar for total time. Add whiskers to each bar to show range of speedups.}}
  \label{Fig:TBvsRAPIDsTahoe_4060_Speedup}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/speedup_vs_norm_time_line_graph_4060.png}
  \caption{Speedup of schedule found by the heuristic vs best schedule found through exhaustive search on NVIDIA RTX 4060 and 
  normalized schedule exploration heuristic exploration time speedup w.r.t full schedule exploration}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
  \caption{Geomean speedup of schedule found by exploration heuristic on NVIDIA T400 and AMD MI2160 vs 
  schedule found by the heuristic on NVIDIA RTX 4060 across batch sizes\TODO{Change the plot labels to say vs 4060 heuristic schedule}}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{figure}
